Proportional multi-state multiple-cohort life table model

### 2018-04-19 MSLT/MSLTdoc.Rmd
Fix variable names

for(sex in i_sex) {
  for (measure in i_measure) {

data <- filter(GBDGL, measure == i_measure, sex == sex, cause == "all causes") %>% select(measure, location, sex, age, metric, cause, val, age_cat, one_rate) 
assign(paste(sex, measure, "interpolated_data", sep = "_"), data)
x=data$age_cat
y=log(data$one_rate)

@@

assign(paste(sex, measure, "interpolated", sep = "_"), interpolated)
plot(interpolated$age,interpolated$rate)

>>>>

for(sex_index in i_sex) {
  for (measure_index in i_measure) {

data <- filter(GBDGL, measure == measure_index, sex == sex_index, cause == "all causes") %>% select(measure, location, sex, age, metric, cause, val, age_cat, one_rate) 
assign(paste(sex_index, measure_index, "interpolated_data", sep = "_"), data)
x=data$age_cat
y=log(data$one_rate)

@@

assign(paste(sex_index, measure_index, "interpolated", sep = "_"), interpolated)
plot(interpolated$age,interpolated$rate)
